\documentclass[a4paper,12pt]{letter}
\usepackage[T1]{fontenc} 
\usepackage[utf8]{inputenc}
\usepackage{eurosym}
\usepackage{graphicx}

%% template: ordine_inglese.tex. Vers. 1.5

((* include 'header.tex' *))

\begin{document}
\topaddr

{\small Pratica N. ((( pratica.numero_pratica ))) }
\vspace{.4cm}

\begin{flushright}
\begin{minipage}{15cm}
To the kind attention of:\\
\hspace*{0.5cm}{\bf ((( pratica.nome_fornitore ))) \\
\hspace*{0.5cm}((( pratica.ind_fornitore ))) }
\end{minipage}
\end{flushright}
\vspace{5mm}

CIG: ((( pratica.cig ))) 

CUP: ((( pratica.cup )))

PURCHASE ORDER N. ~~ ((( pratica.numero_ordine ))) ~~ DATED ~~ ((( pratica.data_ordine )))

The undersigned ((( nome_direttore ))), in
((* if pratica.dir_is_m *))
his
((* else *))
her
((* endif *))
capacity as Director of the ((( sede.sede_uk ))), hereby
awards this contract according to 
article 36 of the Legislative Decree 50/2016
and subsequent amendments and additons,
for the supply/service/work hereunder specified:

\begin{quote}
((( pratica.descrizione_ordine )))
\end{quote}

the total amount is:   
((( pratica.str_costo_ord_uk ))).

((* if pratica.note_ordine *))
{\bf Notes:} ((( pratica.note_ordine )))
((* endif *))
\vspace{1cm}

{\tiny\bf N.B.:
Payment shall be made by wire transfer upon receipt of the goods and 30 days from the presentation of the invoice
and of the enclosed declaration, duly filled in, stamped and signed. \\
For any controversy will prevail the Italian law. \\
The firm / company is aware that if it does not use the bank account indicated above for the financial movements
relating to the contract / purchase order referred to above, the contract / order will be automatically terminated in
accordance with art. 3, paragraph 8 of Law No 136/2010 and subsequent amendments and additions of the Italian
State.
\begin{enumerate}
\item  Please write on your invoice the IBAN or the SWIFT code, which will coincide with what you said to be
dedicated to public procurement of the Italian State.
\item  For the European Companies: Please indicate on your invoice the classification of goods in the Combined
Nomenclature.
\end{enumerate}

For further inquires please contact: ((( pratica.nome_richiedente ))).
}

((* if pratica.dettaglio_ordine *))
\vspace{0.5cm}
\begin{flushright}
Continued ...
\end{flushright}
%%% --ALLEGATI-- 
\newpage
\vspace{2cm}
\quad
((* endif *))

\vspace{1cm}


\begin{minipage}{\textwidth}
\begin{minipage}[t]{8cm}
\begin{center}
The funds' assignee \\
~~ ({}((( pratica.nome_responsabile )))) ~~ \\
\end{center}
\end{minipage}\hfill\begin{minipage}[t]{8cm}
\begin{center}
The Director \\
({}((( titolo_direttore_uk ))) ((( nome_direttore )))) \\
\end{center}
\end{minipage}
\begin{center}
\vspace{14mm}

{\small\bf VAT IT06895721006} \\
{\small Please ship goods and invoice in Largo E. Fermi, 5 Firenze 50125 Italy}
\end{center}
\end{minipage}

\end{document}
